### 2010-03-30 papers/icfp-2010-desc/paper_discussion.tex
Desc@ICFP: use \citet instead of re-writing stuffs.

Generic programming is a vast topic. We refer our reader to Garcia et
al.~\cite{garcia:generic-comparative-study} for a broad overview of
generic support in various languages. In the sole context of Haskell,
there is a myriad of proposals. These approaches are presented and
compared in Hinze et al.~\cite{hinze:generic-approach-comparative} and
Rodriguez et al.~\cite{rodriguez:generic-libs-comparative}.

@@

The interest in generic programming for dependent types is not new
either. Norell~\cite{norell:msc-thesis} have given a formalization of
polytypic programming in the setting of Alfa, a precursor of
Agda. Similarly, Verbruggen et al.~\cite{verbruggen:polytype-prog-coq,
  verbruggen:polytype-coq} have developed a framework for polytypic
programming in the Coq theorem prover. However, these works aim at
\emph{modelling} PolyP or Generic Haskell in a dependently-typed
setting, for the purpose of proving correctness properties of Haskell
code. Our approach is different in that we aim at building a
foundation for data-types, in a dependently-typed theory, for a
dependently-typed system.

Closer to us is the work by Benke et
al.~\cite{benke:universe-generic-prog}. This seminal work introduced
the usage of universes for developing generic programs. Our own
universes are rather similar to theirs: our universe of descriptions
is similar to their universe of iterated induction, and our universe
of indexed descriptions is isomorphic to their universe of finitary
indexed induction. This is not surprising, as we share the same source
of inspiration, namely induction recursion.

>>>>

Generic programming is a vast topic. We refer our reader to
\citet{garcia:generic-comparative-study} for a broad overview of
generic support in various languages. In the sole context of Haskell,
there is a myriad of proposals. These approaches are presented and
compared in \citet{hinze:generic-approach-comparative} and
\citet{rodriguez:generic-libs-comparative}.

@@

The interest in generic programming for dependent types is not new
either. Norell~\cite{norell:msc-thesis} have given a formalization of
polytypic programming in the setting of Alfa, a precursor of
Agda. Similarly, \citet{verbruggen:polytype-prog-coq,
  verbruggen:polytype-coq} have developed a framework for polytypic
programming in the Coq theorem prover. However, these works aim at
\emph{modelling} PolyP or Generic Haskell in a dependently-typed
setting, for the purpose of proving correctness properties of Haskell
code. Our approach is different in that we aim at building a
foundation for data-types, in a dependently-typed theory, for a
dependently-typed system.

Closer to us is the work by \citet{benke:universe-generic-prog}. This
seminal work introduced the usage of universes for developing generic
programs. Our own universes are rather similar to theirs: our universe
of descriptions is similar to their universe of iterated induction,
and our universe of indexed descriptions is isomorphic to their
universe of finitary indexed induction. This is not surprising, as we
share the same source of inspiration, namely induction recursion.
